---
title: "CENT S1-S2 K-Means Clustering on LS Growth"
output:
  html_notebook: default
  html_document: default
---

```{r}
##################################################################################
#inputs: CENT_LS_growth_dct.csv, CENT_LS_growth_dct_spread.csv,
#        CENT_dct_spread_cont_LS_growth.csv, CENT_dct_cont_LS_growth.csv, 
#        CENT_LS_growth_dct_s1_s2.csv
#
#purpose: K-Means clustering (for S1, S2, S1 & S2 normalized separately,
#          and S1 & S2 normalized together)
##################################################################################
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(broom)
library(ggplot2)
library(plotly)
library(factoextra)
library(dtwclust)
library(fpc)
```

# Season 1 Curve Clustering

Using examples from https://cran.r-project.org/web/packages/broom/vignettes/kmeans.html.

```{r}
dct_df <- read.csv("CENT_LS_growth_dct.csv")
dct_spread <- read.csv("CENT_LS_growth_dct_spread.csv")
```

```{r}
cluster_s1 <- dct_spread %>% 
  filter(Season_num == 1) %>%
  ungroup() %>%
  select(-X, -Network, -Season_num, -Show_Name)
```

## General K-Means Clustering

```{r}
set.seed(12)
kclusts_s1 <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_s1, centers = .$k, nstart = 20))

assignments_s1 <- kclusts_s1 %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_s1))
```

### Optimal Number of Clusters

```{r}
fviz_nbclust(cluster_s1, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 4 Clusters (K-Means)

```{r}
clusters4_s1_spread <- assignments_s1 %>% 
  filter(k == 4) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_4 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 1)) 

clusters4_s1 <- merge(clusters4_s1_spread[, c("cluster_kmeans_4", "Show_Name")], 
                      dct_df, by = "Show_Name")

clusters4_s1_plot <- clusters4_s1 %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_4) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters4_s1_plot) %>% 
  layout(title = "Season 1 with 4 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
s1_4clusters <- list(as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 1,]$Show_Name)),
                     as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 2,]$Show_Name)),
                     as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 3,]$Show_Name)), 
                     as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 4,]$Show_Name)))
s1_4clusters
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s2_spread <- dct_spread %>% 
  filter(Season_num == 2) %>%
  ungroup() %>%
  select(-X, -Network, -Season_num)

s2_spread_newcols <- c(paste("X", 101:200, sep = ""))
colnames(s2_spread)[2:ncol(s2_spread)] <- c(s2_spread_newcols)

s1_4clusters_s2_trends <- bind_cols(clusters4_s1_spread, 
                                    s2_spread[, 2:ncol(s2_spread)])

s1_4clusters_s2_trends <- merge(s1_4clusters_s2_trends[, c("cluster_kmeans_4", "Show_Name")], 
                                dct_df, by = "Show_Name")

dct_s1_4clusters_s2_trends <- s1_4clusters_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())

s1_4clusters_s2_trends_plot <- dct_s1_4clusters_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_4, nrow = 4) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(s1_4clusters_s2_trends_plot) %>% 
  layout(title = "Season 1 with 4 K-Means Clusters & Season 2 Trends (LS Growth)", 
         margin = list(t = 150))
```

### 5 Clusters (K-Means)

```{r}
clusters5_s1_spread <- assignments_s1 %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 1)) 

clusters5_s1 <- merge(clusters5_s1_spread[, c("cluster_kmeans_5", "Show_Name")], 
                      dct_df, by = "Show_Name")

clusters5_s1_plot <- clusters5_s1 %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 3) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters5_s1_plot) %>% 
  layout(title = "Season 1 with 5 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
s1_5clusters <- list(as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 1,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 2,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 3,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 4,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 5,]$Show_Name)))
s1_5clusters
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s1_5clusters_s2_trends <- bind_cols(clusters5_s1_spread, 
                                    s2_spread[, 2:ncol(s2_spread)])

s1_5clusters_s2_trends <- merge(s1_5clusters_s2_trends[, c("cluster_kmeans_5", "Show_Name")], 
                                dct_df, by = "Show_Name")

dct_s1_5clusters_s2_trends <- s1_5clusters_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())

s1_5clusters_s2_trends_plot <- dct_s1_5clusters_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 3) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(s1_5clusters_s2_trends_plot) %>% 
  layout(title = "Season 1 with 5 K-Means Clusters & Season 2 Trends (LS Growth)", 
         margin = list(t = 150))
```


----------------------------------------------------------------------------------------------------------
----------------------------------------------------------------------------------------------------------


# Season 2 Curve Clustering

```{r}
cluster_s2 <- dct_spread %>% 
  filter(Season_num == 2) %>%
  ungroup() %>%
  select(-X, -Network, -Season_num, -Show_Name)
```

## General K-Means Clustering

```{r}
set.seed(12)
kclusts_s2 <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_s2, centers = .$k, nstart = 20))

assignments_s2 <- kclusts_s2 %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_s2))
```

### Optimal Number of Clusters

```{r}
fviz_nbclust(cluster_s2, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s2, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s2, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s2, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s2, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s2, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 2 Clusters (K-Means)

```{r}
clusters2_s2_spread <- assignments_s2 %>% 
  filter(k == 2) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_2 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 2)) 

clusters2_s2 <- merge(clusters2_s2_spread[, c("cluster_kmeans_2", "Show_Name")], 
                      dct_df, by = "Show_Name")

clusters2_s2_plot <- clusters2_s2 %>% 
  filter(Season_num == 2) %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_2) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters2_s2_plot) %>% 
  layout(title = "Season 2 with 2 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
s2_2clusters <- list(as.character(unique(clusters2_s2[clusters2_s2$cluster_kmeans_2 == 1,]$Show_Name)),
                     as.character(unique(clusters2_s2[clusters2_s2$cluster_kmeans_2 == 2,]$Show_Name)))
s2_2clusters
```

### 3 Clusters (K-Means)

```{r}
clusters3_s2_spread <- assignments_s2 %>% 
  filter(k == 3) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_3 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 2)) 

clusters3_s2 <- merge(clusters3_s2_spread[, c("cluster_kmeans_3", "Show_Name")], 
                      dct_df, by = "Show_Name")

clusters3_s2_plot <- clusters3_s2 %>% 
  filter(Season_num == 2) %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_3, nrow = 3) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters3_s2_plot) %>% 
  layout(title = "Season 2 with 3 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
s2_3clusters <- list(as.character(unique(clusters3_s2[clusters3_s2$cluster_kmeans_3 == 1,]$Show_Name)),
                     as.character(unique(clusters3_s2[clusters3_s2$cluster_kmeans_3 == 2,]$Show_Name)),
                     as.character(unique(clusters3_s2[clusters3_s2$cluster_kmeans_3 == 3,]$Show_Name)))
s2_3clusters
```

### 5 Clusters (K-Means)

```{r}
clusters5_s2_spread<- assignments_s2 %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 2)) 

clusters5_s2 <- merge(clusters5_s2_spread[, c("cluster_kmeans_5", "Show_Name")], 
                      dct_df, by = "Show_Name")

clusters5_s2_plot <- clusters5_s2 %>% 
  filter(Season_num == 2) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 3) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters5_s2_plot) %>% 
  layout(title = "Season 2 with 5 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
s2_5clusters <- list(as.character(unique(clusters5_s2[clusters5_s2$cluster_kmeans_5 == 1,]$Show_Name)),
                     as.character(unique(clusters5_s2[clusters5_s2$cluster_kmeans_5 == 2,]$Show_Name)),
                     as.character(unique(clusters5_s2[clusters5_s2$cluster_kmeans_5 == 3,]$Show_Name)),
                     as.character(unique(clusters5_s2[clusters5_s2$cluster_kmeans_5 == 4,]$Show_Name)),
                     as.character(unique(clusters5_s2[clusters5_s2$cluster_kmeans_5 == 5,]$Show_Name)))
s2_5clusters
```


----------------------------------------------------------------------------------------------------------
----------------------------------------------------------------------------------------------------------


# S1-S2 Non-Continuous Curve Clustering

```{r}
temp1 <- filter(dct_spread, Season_num == 1)
temp2 <- filter(dct_spread, Season_num == 2)
temp2_newcols <- c(paste("X", 101:200, sep = ""))
colnames(temp2)[5:ncol(temp2)] <- c(temp2_newcols)

dct_spread_s1_s2 <- bind_cols(temp1, temp2[, 5:ncol(temp2)])
rm(temp1, temp2, temp2_newcols)

cluster_s1_s2 <- dct_spread_s1_s2 %>%
  select(-X, -Network, -Season_num, -Show_Name)

dct_s1_s2 <- read.csv("CENT_LS_growth_dct_s1_s2.csv")
```

## General K-Means Clustering

```{r}
set.seed(12)
kclusts_s1_s2 <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_s1_s2, centers = .$k, nstart = 20))

assignments_s1_s2 <- kclusts_s1_s2 %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_s1_s2))
```

### Optimal Number of Clusters

```{r}
fviz_nbclust(cluster_s1_s2, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_s2, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_s2, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_s2, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```


```{r}
fviz_nbclust(cluster_s1_s2, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_s2, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 3 Clusters (K-Means)

```{r}
clusters3_s1_s2_spread <- assignments_s1_s2 %>% 
  filter(k == 3) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_3 = .cluster) %>% 
  bind_cols(dct_spread_s1_s2) 

clusters3_s1_s2 <- merge(clusters3_s1_s2_spread[, c("cluster_kmeans_3", "Show_Name")], 
                         dct_s1_s2, by = "Show_Name")

clusters3_s1_s2_plot <- clusters3_s1_s2 %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_3, nrow = 3) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters3_s1_s2_plot) %>% 
  layout(title = "S1-S2 (Non-Continuous) with 3 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

```{r}
s1_s2_3clusters <- list(as.character(unique(clusters3_s1_s2[clusters3_s1_s2$cluster_kmeans_3 == 1,]$Show_Name)),
                        as.character(unique(clusters3_s1_s2[clusters3_s1_s2$cluster_kmeans_3 == 2,]$Show_Name)),
                        as.character(unique(clusters3_s1_s2[clusters3_s1_s2$cluster_kmeans_3 == 3,]$Show_Name)))
s1_s2_3clusters
```

### 5 Clusters (K-Means)

```{r}
clusters5_s1_s2_spread <- assignments_s1_s2 %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(dct_spread_s1_s2) 

clusters5_s1_s2 <- merge(clusters5_s1_s2_spread[, c("cluster_kmeans_5", "Show_Name")], 
                         dct_s1_s2, by = "Show_Name")

clusters5_s1_s2_plot <- clusters5_s1_s2 %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 3) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters5_s1_s2_plot) %>% 
  layout(title = "S1-S2 (Non-Continuous) with 5 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

```{r}
s1_s2_5clusters <- list(as.character(unique(clusters5_s1_s2[clusters5_s1_s2$cluster_kmeans_5 == 1,]$Show_Name)),
                        as.character(unique(clusters5_s1_s2[clusters5_s1_s2$cluster_kmeans_5 == 2,]$Show_Name)),
                        as.character(unique(clusters5_s1_s2[clusters5_s1_s2$cluster_kmeans_5 == 3,]$Show_Name)),
                        as.character(unique(clusters5_s1_s2[clusters5_s1_s2$cluster_kmeans_5 == 4,]$Show_Name)),
                        as.character(unique(clusters5_s1_s2[clusters5_s1_s2$cluster_kmeans_5 == 5,]$Show_Name)))
s1_s2_5clusters
```


----------------------------------------------------------------------------------------------------------
----------------------------------------------------------------------------------------------------------


#S1-S2 Continuous Curve Clustering

```{r}
dct_cont <- read.csv("CENT_dct_cont_LS_growth.csv")
dct_spread_cont <- read.csv("CENT_dct_spread_cont_LS_growth.csv")
cluster_cont <- dct_spread_cont %>%
  select(-X, -Network, -Show_Name)
```

## General K-Means Clustering

```{r}
set.seed(12)
kclusts_cont <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_cont, centers = .$k, nstart = 20))

assignments_cont <- kclusts_cont %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_cont))
```

### Optimal Number of Clusters

```{r}
fviz_nbclust(cluster_cont, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_cont, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_cont, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_cont, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_cont, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_cont, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 2 Clusters (K-Means)

```{r}
clusters2_cont_spread <- assignments_cont %>% 
  filter(k == 2) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_2 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 2)) 

clusters2_cont <- merge(clusters2_cont_spread[, c("cluster_kmeans_2", "Show_Name")], 
                      dct_cont, by = "Show_Name")

clusters2_cont_plot <- clusters2_cont %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_2) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters2_cont_plot) %>% 
  layout(title = "S1-S2 (Continuous) with 2 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
cont_2clusters <- list(as.character(unique(clusters2_cont[clusters2_cont$cluster_kmeans_2 == 1,]$Show_Name)),
                       as.character(unique(clusters2_cont[clusters2_cont$cluster_kmeans_2 == 2,]$Show_Name)))
cont_2clusters
```

### 3 Clusters (K-Means)

```{r}
clusters3_cont_spread <- assignments_cont %>% 
  filter(k == 3) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_3 = .cluster) %>% 
  bind_cols(dct_spread_cont) 

clusters3_cont <- merge(clusters3_cont_spread[, c("cluster_kmeans_3", "Show_Name")], 
                          dct_cont, by = "Show_Name")

clusters3_cont_plot <- clusters3_cont %>%
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_3, nrow = 3) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters3_cont_plot) %>% 
  layout(title = "S1-S2 (Continuous) with 3 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
cont_3clusters <- list(as.character(unique(clusters3_cont[clusters3_cont$cluster_kmeans_3 == 1,]$Show_Name)),
                       as.character(unique(clusters3_cont[clusters3_cont$cluster_kmeans_3 == 2,]$Show_Name)),
                       as.character(unique(clusters3_cont[clusters3_cont$cluster_kmeans_3 == 3,]$Show_Name)))
cont_3clusters
```

### 5 Clusters (K-Means)

```{r}
clusters5_cont_spread <- assignments_cont %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(dct_spread_cont) 

clusters5_cont <- merge(clusters5_cont_spread[, c("cluster_kmeans_5", "Show_Name")], 
                          dct_cont, by = "Show_Name")

clusters5_cont_plot <- clusters5_cont %>%
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 3) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters5_cont_plot) %>% 
  layout(title = "S1-S2 (Continuous) with 5 K-Means Clusters (LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
cont_5clusters <- list(as.character(unique(clusters5_cont[clusters5_cont$cluster_kmeans_5 == 1,]$Show_Name)),
                       as.character(unique(clusters5_cont[clusters5_cont$cluster_kmeans_5 == 2,]$Show_Name)),
                       as.character(unique(clusters5_cont[clusters5_cont$cluster_kmeans_5 == 3,]$Show_Name)),
                       as.character(unique(clusters5_cont[clusters5_cont$cluster_kmeans_5 == 4,]$Show_Name)),
                       as.character(unique(clusters5_cont[clusters5_cont$cluster_kmeans_5 == 5,]$Show_Name)))
cont_5clusters
```

# Diagnostics
 
```{r}
# create distance matrices for clusters
kmeans_s1_4cl_growth_d <- dist(clusters4_s1_spread[, 6:105])
kmeans_s1_5cl_growth_d <- dist(clusters5_s1_spread[, 6:105])
kmeans_s2_3cl_growth_d <- dist(clusters3_s2_spread[, 6:105])
kmeans_s2_2cl_growth_d <- dist(clusters2_s2_spread[, 6:105])
kmeans_s2_5cl_growth_d <- dist(clusters5_s2_spread[, 6:105])
kmeans_s1_s2_3cl_growth_d <- dist(clusters3_s1_s2_spread[, 6:205])
kmeans_s1_s2_5cl_growth_d <- dist(clusters5_s1_s2_spread[, 6:205])
kmeans_cont_3cl_growth_d <- dist(clusters3_cont_spread[, 5:104])
kmeans_cont_2cl_growth_d <- dist(clusters2_s2_spread[, 6:105])
kmeans_cont_5cl_grwoth_d <- dist(clusters5_cont_spread[, 5:104])

# diagnostics
diagnostics_LS_growth_kmeans_s1_4cl <- cluster.stats(kmeans_s1_4cl_growth_d, as.numeric(clusters4_s1_spread$cluster_kmeans_4))
diagnostics_LS_growth_kmeans_s1_5cl <- cluster.stats(kmeans_s1_5cl_growth_d, as.numeric(clusters5_s1_spread$cluster_kmeans_5))
diagnostics_LS_growth_kmeans_s2_3cl <- cluster.stats(kmeans_s2_3cl_growth_d, as.numeric(clusters3_s2_spread$cluster_kmeans_3))
diagnostics_LS_growth_kmeans_s2_2cl <- cluster.stats(kmeans_s2_2cl_growth_d, as.numeric(clusters2_s2_spread$cluster_kmeans_2))
diagnostics_LS_growth_kmeans_s2_5cl <- cluster.stats(kmeans_s2_5cl_growth_d, as.numeric(clusters5_s2_spread$cluster_kmeans_5))
diagnostics_LS_growth_kmeans_sep_3cl <- cluster.stats(kmeans_s1_s2_3cl_growth_d, as.numeric(clusters3_s1_s2_spread$cluster_kmeans_3))
diagnostics_LS_growth_kmeans_sep_5cl <- cluster.stats(kmeans_s1_s2_5cl_growth_d, as.numeric(clusters5_s1_s2_spread$cluster_kmeans_5))
diagnostics_LS_growth_kmeans_cont_3cl <- cluster.stats(kmeans_cont_3cl_growth_d, as.numeric(clusters3_cont_spread$cluster_kmeans_3))
diagnostics_LS_growth_kmeans_cont_2cl <- cluster.stats(kmeans_cont_2cl_growth_d, as.numeric(clusters2_cont_spread$cluster_kmeans_2))
diagnostics_LS_growth_kmeans_cont_5cl <- cluster.stats(kmeans_cont_5cl_grwoth_d, as.numeric(clusters5_cont_spread$cluster_kmeans_5))

# gather diagnostic names and list all diagnostics objects
d_names <- ls()[grep("diagnostics", ls())]
d_list <- mget(ls()[grep("diagnostics", ls())])

# generate df with statsitics of interest for comparison
diagnostic_df <- as.data.frame(NA)

for (n in 1:length(d_names)){
  diagnostic_df[n, 1] <- paste(d_names[n])
  diagnostic_df[n, 2] <- d_list[[n]]["average.between"]
  diagnostic_df[n, 3] <- d_list[[n]]["average.within"]
  diagnostic_df[n, 4] <- d_list[[n]]["wb.ratio"]
  diagnostic_df[n, 5] <- d_list[[n]]["widestgap"]
  diagnostic_df[n, 6] <- d_list[[n]]["dunn2"]
  diagnostic_df[n, 7] <- d_list[[n]]["avg.silwidth"]
  diagnostic_df[n, 8] <- d_list[[n]]["within.cluster.ss"]
  diagnostic_df[n, 9] <- d_list[[n]]["cluster.number"]
}

# add information for decision making
colnames(diagnostic_df)[1] <- "name"

diagnostic_df$name <- sub("diagnostics_", "", diagnostic_df$name)

diagnostic_df$algorithm <- ifelse(grepl("kmeans", diagnostic_df$name) == 1, "kmeans",
                                  ifelse(grepl("kshape", diagnostic_df$name) == 1, "kshape",
                                         ifelse(grepl("PCA", diagnostic_df$name) == 1, "PCA",
                                                ifelse(grepl("tadpole", diagnostic_df$name) == 1, "tadpole",
                                                       ifelse(grepl("dtw", diagnostic_df$name) == 1, "DTW", 0)))))

diagnostic_df$season <- ifelse(grepl("s1", diagnostic_df$name) == 1, "s1",
                               ifelse(grepl("s2", diagnostic_df$name) == 1, "s2",
                                      ifelse(grepl("sep", diagnostic_df$name) == 1, "sep",
                                             ifelse(grepl("cont", diagnostic_df$name) == 1, "cont", 0))))

diagnostic_df$stream <- ifelse(grepl("C3", diagnostic_df$name) == 1, "C3",
                               ifelse(grepl("LS", diagnostic_df$name) == 1, "LS", 0))

diagnostic_df$data <- ifelse(grepl("raw", diagnostic_df$name) == 1, "raw",
                             ifelse(grepl("growth", diagnostic_df$name) == 1, "growth",
                                    ifelse(grepl("rebase", diagnostic_df$name) == 1, "rebase",0)))
```

```{r}
# write table
write.csv(diagnostic_df, "diagnostics_LS_growth_kmeans.csv")
```