---
author: "CENT S1 Raw Clusters. Raw Impressions/Normalized. Best Matches on S2. Detail."
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    source_code: embed
---

```{r}
##########################################################
#
# Inputs: s1_s2_data.csv, dct_C3_raw_cont.csv, 
#         dct_C3_growth_cont.csv, 
#         s1_shows_best_clusters_and_matches.csv
#
# Purpose: Detailed trends of C3 impressions and Growth,
#          Season two graphs include only cases that either
#          [1] are intersections of the best other cluster
#          matches, or [2] are intersections of the best other
#          Season 2 alone clusters
#
##########################################################
```

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(plotly)
library(scales)
```

```{r}
df <- read.csv("s1_s2_data.csv") %>% select(-X) %>% filter(Episode_num < 15)
df_dct <- read.csv("dct_C3_raw_cont.csv") %>% select(-X)
df_dct_growth <- read.csv("dct_C3_growth_cont.csv") %>% select(-X)
s1_shows_best_clusters_and_matches <- read.csv("s1_shows_best_clusters_and_matches.csv")
matches_only <- read.csv("s1_shows_best_clusters_and_matches.csv") %>% 
  select(Show_Name, C3_raw_best_matches, C3_raw_best_matches_S2, 
         C3_growth_best_matches, C3_growth_best_matches_S2)

df <- merge(df, matches_only)
df_dct <- merge(df_dct, s1_shows_best_clusters_and_matches)
df_dct_growth <- merge(df_dct_growth, s1_shows_best_clusters_and_matches)
```

```{r}
my_theme <-  theme(panel.background = element_blank(), 
                   panel.grid.major = element_line(color = "#d8d8d8", linetype = "dotted"), 
                   panel.grid.major.x = element_blank(), 
                   plot.title = element_text(hjust = 0.5),
                   axis.title.y = element_blank(),
                   axis.line.y = element_blank(),
                   axis.ticks.y = element_blank(),
                   axis.line.x = element_line(color = "#d8d8d8", linetype = "dashed"),
                   strip.background = element_blank())
```

C3 Raw S1 Clusters. Best Match
====================

Row {.tabset}
---------------------------------------

### Raw Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 1, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 2, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 3, Season_num == 1 | Season_num == 2& !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 4, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
 coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 5, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 5",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

Row {.tabset}
---------------------------------------

### Normalized Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 1, period <= 50 | period > 50 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 2, period <= 50 | period > 50 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 3, period <= 50 | period > 50 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))


```

### Normalized Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 4, period <= 50 | period > 50 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))

```


### Normalized Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 5, period <= 50 | period > 50 & !is.na(C3_raw_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))
```



C3 Raw S1 Clusters. S1-S2. Best S2 Match
====================

Row {.tabset}
---------------------------------------

### Raw Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 1, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 2, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 3, Season_num == 1 | Season_num == 2& !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 4, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
 coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 5, Season_num == 1 | Season_num == 2 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Impressions, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Impressions, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 1500000), xlim = c(1, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Cluster 5",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

Row {.tabset}
---------------------------------------

### Normalized Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 1, period <= 50 | period > 50 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 2, period <= 50 | period > 50 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 3, period <= 50 | period > 50 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))


```

### Normalized Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 4, period <= 50 | period > 50 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))

```


### Normalized Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct %>% filter(is.na(C3_raw_cluster) == F, C3_raw_cluster == 5, period <= 50 | period > 50 & !is.na(C3_raw_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2  Raw Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))
```


C3 Growth S1 Clusters. Best Match
====================

Row {.tabset}
---------------------------------------

### Raw Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 1, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 2, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 3, Season_num == 1 | Season_num == 2& !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 4, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
 coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 5, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 5",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

Row {.tabset}
---------------------------------------

### Normalized Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 1, period <= 50 | period > 50 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 2, period <= 50 | period > 50 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 3, period <= 50 | period > 50 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))


```

### Normalized Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 4, period <= 50 | period > 50 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))

```


### Normalized Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 5, period <= 50 | period > 50 & !is.na(C3_growth_best_matches))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))
```



C3 Growth S1 Clusters. S1-S2. Best S2 Match
====================

Row {.tabset}
---------------------------------------

### Raw Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 1, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 2, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 3, Season_num == 1 | Season_num == 2& !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 4, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
 coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Raw Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 5, Season_num == 1 | Season_num == 2 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = Episode_num, y = C3_Growth, color = Show_Name)) +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Linear"), 
              color = "black", se = F, method = lm, linetype = "dashed") +
  geom_smooth(aes(x = Episode_num, y = C3_Growth, alpha = "Smooth"), 
              color = "#747677", se = F, linetype = "dotted") +
  labs(x = "Episode Number") +
  scale_y_continuous(labels = comma) +
  coord_cartesian(ylim = c(0, 3), xlim = c(2, 13)) +
  facet_wrap(~ Season_num) +
  theme(panel.spacing = unit(0, "lines")) +
  my_theme

ggplotly(C3_raw) %>% 
  layout(title = "C3 Impressions, S1-S2 Growth Cluster 5",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

Row {.tabset}
---------------------------------------

### Normalized Cluster 1

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 1, period <= 50 | period > 50 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 1",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 2

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 2, period <= 50 | period > 50 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 2",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 3

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 3, period <= 50 | period > 50 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 3",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100, 
                       t = 50))
```

### Normalized Cluster 4

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 4, period <= 50 | period > 50 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))
```


### Normalized Cluster 5

```{r, fig.align = 'center'}
C3_raw <- ggplot(df_dct_growth %>% filter(is.na(C3_growth_cluster) == F, C3_growth_cluster == 5, period <= 50 | period > 50 & !is.na(C3_growth_best_matches_S2))) +
  geom_line(aes(x = period, y = dct_values, color = Show_Name)) +
  scale_y_continuous(labels = comma) +
  my_theme 

ggplotly(C3_raw) %>% 
  layout(title = "C3 Normalized Impressions, S1-S2 Growth Cluster 4",
         autosize = FALSE, width = 1700, height = 500, 
         margin = list(l = 150, 
                       r = 50, 
                       b = 100,
                       t = 50))
```
