---
title: "CENT S1 K-Means Clustering on C3 & LS Growth Appended, Differences, and Averages"
output:
  html_notebook: default
  html_document: default
---

```{r}
##################################################################################
# inputs: dct_C3_LS_growth.csv, dct_spread_C3_LS_growth.csv, 
#         dct_C3_LS_diff_growth.csv.csv, dct_spread_C3_LS_diff_growth.csv, 
#         dct_C3_LS_avg_growth.csv.csv, dct_spread_C3_LS_avg_growth.csv
#
# purpose: K-Means clustering for CENT S1 using C3 and LS appended,
#          C3-LS (difference) normalized, and C3 & LS averaged normalized
##################################################################################
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(broom)
library(ggplot2)
library(plotly)
library(factoextra)
library(dtwclust)
library(fpc)
```

# S1 Curve Clustering on C3 & LS Normalized Separately and Appended

Using examples from https://cran.r-project.org/web/packages/broom/vignettes/kmeans.html.

```{r}
#read in long and wide format data
dct_df <- read.csv("dct_C3_LS_growth.csv") %>% select(-X)
dct_spread <- read.csv("dct_spread_C3_LS_growth.csv") %>% select(-X)
```

```{r}
#filter wide data to only cluster on season 1
cluster_s1 <- dct_spread %>% 
  filter(Season_num == 1) %>%
  ungroup() %>%
  select(-Network, -Season_num, -Show_Name)
```

## General K-Means Clustering

```{r}
#explore the effect of clustering on between 1 and 5 clusters 
#(perform clustering 5 times, each time using value 1 through 5)
set.seed(12)
kclusts_s1 <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_s1, centers = .$k, nstart = 20))

#add each cluster classification to the original season 1 dataset
assignments_s1 <- kclusts_s1 %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_s1))
```

### Optimal Number of Clusters

```{r}
#elbow method representing the variance within each cluster (total within sum of squares)
#the bend (or elbow) indicates that clusters beyond that point have little additional value
fviz_nbclust(cluster_s1, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
#optimal number of clusters using average silhouette
#a measure of how similar the object is to its own cluster compared to others
fviz_nbclust(cluster_s1, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
#optimal number of clusters using gap statistics
#compares change in within-cluster dispersion with expected from null distribution
fviz_nbclust(cluster_s1, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
#optimal number of clusters using partitioning around mediods and gap statistic
fviz_nbclust(cluster_s1, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
#optimal number of clusters using hierarchical clustering
#using Euclidean distance to calculate dissimilarities between observations
fviz_nbclust(cluster_s1, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
#optimal number of clusters using hierarchical clustering
#using Pearson correlation as distance measure
fviz_nbclust(cluster_s1, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 4 Clusters (K-Means)

```{r}
#bind selected K number of clusters to both sets of data with normalized dct values and visualize
clusters4_s1_spread <- assignments_s1 %>% 
  filter(k == 4) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_4 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 1)) 

clusters4_s1 <- merge(clusters4_s1_spread[, c("cluster_kmeans_4", "Show_Name")], 
                      dct_df, by = "Show_Name")

write.csv(clusters4_s1, "kmeans_C3_LS_growth_s1_4cl.csv")
```

```{r}
clusters4_s1_plot <- clusters4_s1 %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_4) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters4_s1_plot) %>% 
  layout(title = "Season 1 with 4 K-Means Clusters (C3 & LS Growth)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
#list names of shows in each cluster
s1_4clusters <- list(as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 1,]$Show_Name)),
                     as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 2,]$Show_Name)),
                     as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 3,]$Show_Name)), 
                     as.character(unique(clusters4_s1[clusters4_s1$cluster_kmeans_4 == 4,]$Show_Name)))
s1_4clusters
```

```{r}
# GROUPINGS BY CLUSTER

#same plot as before, but legend is grouped by cluster for easier distinction
by_cluster_4kmeans <- clusters4_s1 %>% 
  filter(Season_num == 1) %>% 
  plot_ly(x = ~period, 
         y = ~dct_values, 
         color = ~Show_Name,
         yaxis = ~paste0('y', cluster_kmeans_4), 
         legendgroup = ~cluster_kmeans_4) %>% 
  add_lines() %>% 
  subplot(nrows = 4, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 4 K-Means Clusters (C3 & LS Growth)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
by_cluster_4kmeans
```

### 5 Clusters (K-Means)

```{r}
#same code as with 5 clusters
clusters5_s1_spread <- assignments_s1 %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(filter(dct_spread, Season_num == 1)) 

clusters5_s1 <- merge(clusters5_s1_spread[, c("cluster_kmeans_5", "Show_Name")], 
                      dct_df, by = "Show_Name")

write.csv(clusters5_s1, "kmeans_C3_LS_growth_s1_5cl.csv")
```

```{r}
clusters5_s1_plot <- clusters5_s1 %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 3) +  
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(clusters5_s1_plot) %>% 
  layout(title = "Season 1 with 5 K-Means Clusters (C3 & LS)", 
         margin = list(t = 150))
```

#### List Show Names within Clusters

```{r}
s1_5clusters <- list(as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 1,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 2,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 3,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 4,]$Show_Name)), 
                     as.character(unique(clusters5_s1[clusters5_s1$cluster_kmeans_5 == 5,]$Show_Name)))
s1_5clusters
```

```{r}
# GROUPINGS BY CLUSTER
by_cluster_5kmeans <- clusters5_s1 %>% 
  filter(Season_num == 1) %>% 
  plot_ly(x = ~period, 
         y = ~dct_values, 
         color = ~Show_Name,
         yaxis = ~paste0('y', cluster_kmeans_5), 
         legendgroup = ~cluster_kmeans_5) %>% 
  add_lines() %>% 
  subplot(nrows = 5, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 5 K-Means Clusters (C3 & LS)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
by_cluster_5kmeans
```


----------------------------------------------------------------------------------------------------------
----------------------------------------------------------------------------------------------------------


# S1 Curve Clustering on C3-LS Differences

```{r}
#same code for clustering as before
dct_df_diff <- read.csv("dct_C3_LS_diff_growth.csv") %>% select(-X)
dct_spread_diff <- read.csv("dct_spread_C3_LS_diff_growth.csv") %>% select(-X)
```

```{r}
cluster_s1_diff <- dct_spread_diff %>% 
  filter(Season_num == 1) %>%
  ungroup() %>%
  select(-Network, -Season_num, -Show_Name)
```

## General K-Means Clustering

```{r}
set.seed(12)
kclusts_s1_diff <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_s1_diff, centers = .$k, nstart = 20))

assignments_s1_diff <- kclusts_s1_diff %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_s1_diff))
```

### Optimal Number of Clusters

```{r}
fviz_nbclust(cluster_s1_diff, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_diff, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_diff, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_diff, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_diff, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_diff, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 3 Clusters (K-Means)

```{r}
clusters3_s1_diff_spread<- assignments_s1_diff %>% 
  filter(k == 3) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_3 = .cluster) %>% 
  bind_cols(filter(dct_spread_diff, Season_num == 1)) 

clusters3_s1_diff <- merge(clusters3_s1_diff_spread[, c("cluster_kmeans_3", "Show_Name")], 
                           dct_df_diff, by = "Show_Name")

clusters3_s1_diff_plot <- clusters3_s1_diff %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_3, nrow = 3) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

s1_diff_3kmeans <- ggplotly(clusters3_s1_diff_plot) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 3 K-Means Clusters (C3-LS Differences)", 
         autosize = FALSE, width = 550, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_diff_3kmeans
```

#### List Show Names within Clusters

```{r}
s1_diff_3clusters <- list(as.character(unique(clusters3_s1_diff[clusters3_s1_diff$cluster_kmeans_3 == 1,]$Show_Name)),
                          as.character(unique(clusters3_s1_diff[clusters3_s1_diff$cluster_kmeans_3 == 2,]$Show_Name)),
                          as.character(unique(clusters3_s1_diff[clusters3_s1_diff$cluster_kmeans_3 == 3,]$Show_Name)))
s1_diff_3clusters
```

### 4 Clusters (K-Means)

```{r}
clusters4_s1_diff_spread<- assignments_s1_diff %>% 
  filter(k == 4) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_4 = .cluster) %>% 
  bind_cols(filter(dct_spread_diff, Season_num == 1)) 

clusters4_s1_diff <- merge(clusters4_s1_diff_spread[, c("cluster_kmeans_4", "Show_Name")], 
                           dct_df_diff, by = "Show_Name")

clusters4_s1_diff_plot <- clusters4_s1_diff %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_4) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

s1_diff_4kmeans <- ggplotly(clusters4_s1_diff_plot) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 4 K-Means Clusters (C3-LS Differences)", 
         autosize = FALSE, width = 550, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_diff_4kmeans
```

#### List Show Names within Clusters

```{r}
s1_diff_4clusters <- list(as.character(unique(clusters4_s1_diff[clusters4_s1_diff$cluster_kmeans_4 == 1,]$Show_Name)),
                          as.character(unique(clusters4_s1_diff[clusters4_s1_diff$cluster_kmeans_4 == 2,]$Show_Name)),
                          as.character(unique(clusters4_s1_diff[clusters4_s1_diff$cluster_kmeans_4 == 3,]$Show_Name)), 
                          as.character(unique(clusters4_s1_diff[clusters4_s1_diff$cluster_kmeans_4 == 4,]$Show_Name)))
s1_diff_4clusters
```

### 5 Clusters (K-Means)

```{r}
clusters5_s1_diff_spread<- assignments_s1_diff %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(filter(dct_spread_diff, Season_num == 1)) 

clusters5_s1_diff <- merge(clusters5_s1_diff_spread[, c("cluster_kmeans_5", "Show_Name")], 
                      dct_df_diff, by = "Show_Name")

write.csv(clusters5_s1_diff, "kmeans_C3_LS_growth_diff_s1_5cl.csv")
```

```{r}
clusters5_s1_diff_plot <- clusters5_s1_diff %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 5) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

s1_diff_5kmeans <- ggplotly(clusters5_s1_diff_plot) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 5 K-Means Clusters (C3-LS Differences)", 
         autosize = FALSE, width = 550, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_diff_5kmeans
```

#### List Show Names within Clusters

```{r}
s1_diff_5clusters <- list(as.character(unique(clusters5_s1_diff[clusters5_s1_diff$cluster_kmeans_5 == 1,]$Show_Name)),
                          as.character(unique(clusters5_s1_diff[clusters5_s1_diff$cluster_kmeans_5 == 2,]$Show_Name)),
                          as.character(unique(clusters5_s1_diff[clusters5_s1_diff$cluster_kmeans_5 == 3,]$Show_Name)),
                          as.character(unique(clusters5_s1_diff[clusters5_s1_diff$cluster_kmeans_5 == 4,]$Show_Name)),
                          as.character(unique(clusters5_s1_diff[clusters5_s1_diff$cluster_kmeans_5 == 5,]$Show_Name)))
s1_diff_5clusters
```

```{r}
# S1 CLUSTERS & S2 TRENDS

#create subset of show curves from season 2
s2_spread <- dct_spread_diff %>% 
  filter(Season_num == 2) %>%
  ungroup() %>%
  select(-Network, -Season_num)

#change column names range to append to season 1 curves with cluster variable
s2_spread_newcols <- c(paste("X", 101:200, sep = ""))
colnames(s2_spread)[2:ncol(s2_spread)] <- c(s2_spread_newcols)

s1_diff_5clusters_s2_trends <- bind_cols(clusters5_s1_diff_spread, 
                                         s2_spread[, 2:ncol(s2_spread)])

s1_diff_5clusters_s2_trends <- merge(s1_diff_5clusters_s2_trends[, c("cluster_kmeans_5", "Show_Name")], 
                                     dct_df_diff, by = "Show_Name")

#re-number rows to make continuous over 200 periods for both seasons
dct_s1_diff_5clusters_s2_trends <- s1_diff_5clusters_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())

write.csv(dct_s1_diff_5clusters_s2_trends, "kmeans_C3_LS_growth_diff_s1_5cl_s2trends.csv")
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s1_diff_5clusters_s2_trends_plot <- dct_s1_diff_5clusters_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 5) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "#d8d8d8", 
                                        linetype = "dotted"), 
        strip.background = element_blank())

s1_diff_5kmeans_s2trends <- ggplotly(s1_diff_5clusters_s2_trends_plot) %>% 
  layout(title = "Season 1 with 5 K-Means Clusters & Season 2 Trends (C3-LS Differences)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_diff_5kmeans_s2trends
```

```{r}
# GROUPINGS BY CLUSTER

#same plot as before, but legend is grouped by cluster for easier distinction
by_cluster_5kmeans_diff <- plot_ly(dct_s1_diff_5clusters_s2_trends, 
        x = ~period, 
        y = ~dct_values, 
        color = ~Show_Name,
        yaxis = ~paste0('y', cluster_kmeans_5), 
        legendgroup = ~cluster_kmeans_5) %>% 
  add_lines() %>% 
  subplot(nrows = 5, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 5 K-Means Clusters & Season 2 Trends (C3-LS Differences)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
by_cluster_5kmeans_diff
```

```{r}
# S1-S2 Trends Clustered on S1 Clusters

#merge season 1 cluster data frame and continuous trends data frame
#to visualize season 1 and season 2 normalized continuously
#and clustered on season 1 clusters
dct_spread_diff_cont <- read.csv("dct_spread_C3_LS_diff_growth_cont.csv") %>% select(-X)
dct_diff_cont <- read.csv("dct_C3_LS_diff_growth_cont.csv")

season1_kmeans5_clusters <- clusters5_s1_diff_spread %>% 
  select(Show_Name, cluster_kmeans_5) %>% 
  rename(s1_cluster = cluster_kmeans_5)

s1_clusters_cont_trends <- merge(season1_kmeans5_clusters, 
                                 dct_spread_diff_cont, by = "Show_Name")

s1_clusters_cont_trends <- merge(s1_clusters_cont_trends[, c("Show_Name", "s1_cluster")], 
                                 dct_diff_cont, by = "Show_Name") %>% select(-X)

write.csv(s1_clusters_cont_trends, "kmeans_C3_LS_growth_diff_s1_5cl_cont_trends.csv") 
```

```{r}
# Plot for Continuous Trends Clustered on S1 Clusters
s1_clusters_cont_trends_plot <- plot_ly(s1_clusters_cont_trends, 
        x = ~period, 
        y = ~dct_values, 
        color = ~Show_Name,
        yaxis = ~paste0('y', s1_cluster), 
        legendgroup = ~s1_cluster) %>% 
  add_lines() %>% 
  subplot(nrows = 5, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "S1-S2 Clustered on S1 Clusters (C3 + LS Growth Differences)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))

s1_clusters_cont_trends_plot
```


----------------------------------------------------------------------------------------------------------
----------------------------------------------------------------------------------------------------------

# S1 Curve Clustering on C3 & LS Averages

```{r}
#same code for clustering as before
dct_df_avg <- read.csv("dct_C3_LS_avg_growth.csv") %>% select(-X)
dct_spread_avg <- read.csv("dct_spread_C3_LS_avg_growth.csv") %>% select(-X)
```

```{r}
cluster_s1_avg <- dct_spread_avg %>% 
  filter(Season_num == 1) %>%
  ungroup() %>%
  select(-Network, -Season_num, -Show_Name)
```

## General K-Means Clustering

```{r}
set.seed(12)
kclusts_s1_avg <- data.frame(k = 1:5) %>% 
  group_by(k) %>% 
  do(kclust = kmeans(cluster_s1_avg, centers = .$k, nstart = 20))

assignments_s1_avg <- kclusts_s1_avg %>% group_by(k) %>% do(augment(.$kclust[[1]], cluster_s1_avg))
```

### Optimal Number of Clusters

```{r}
fviz_nbclust(cluster_s1_avg, 
             kmeans, 
             method = "wss",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_avg, 
             kmeans, 
             method = "silhouette",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_avg, 
             kmeans, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_avg, 
             cluster::pam, 
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_avg, 
             hcut, 
             hc_method = "single",
             hc_metric = "euclidean",
             method = "gap_stat",
             k.max = 5)
```

```{r}
fviz_nbclust(cluster_s1_avg, 
             hcut, 
             hc_method = "single",
             hc_metric = "pearson",
             method = "silhouette",
             k.max = 5,
             nboot = 500)
```

### 4 Clusters (K-Means)

```{r}
clusters4_s1_avg_spread<- assignments_s1_avg %>% 
  filter(k == 4) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_4 = .cluster) %>% 
  bind_cols(filter(dct_spread_avg, Season_num == 1)) 

clusters4_s1_avg <- merge(clusters4_s1_avg_spread[, c("cluster_kmeans_4", "Show_Name")], 
                          dct_df_avg, by = "Show_Name")

clusters4_s1_avg_plot <- clusters4_s1_avg %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_4) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

s1_avg_4kmeans <- ggplotly(clusters4_s1_avg_plot) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 4 K-Means Clusters (C3 & LS Averages)", 
         autosize = FALSE, width = 550, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_avg_4kmeans
```

#### List Show Names within Clusters

```{r}
s1_avg_4clusters <- list(as.character(unique(clusters4_s1_avg[clusters4_s1_avg$cluster_kmeans_4 == 1,]$Show_Name)),
                         as.character(unique(clusters4_s1_avg[clusters4_s1_avg$cluster_kmeans_4 == 2,]$Show_Name)),
                         as.character(unique(clusters4_s1_avg[clusters4_s1_avg$cluster_kmeans_4 == 3,]$Show_Name)),
                         as.character(unique(clusters4_s1_avg[clusters4_s1_avg$cluster_kmeans_4 == 4,]$Show_Name)))
s1_avg_4clusters
```

```{r}
# S1 CLUSTERS & S2 TRENDS
s2_spread <- dct_spread_avg %>% 
  filter(Season_num == 2) %>%
  ungroup() %>%
  select(-Network, -Season_num)

s2_spread_newcols <- c(paste("X", 101:200, sep = ""))
colnames(s2_spread)[2:ncol(s2_spread)] <- c(s2_spread_newcols)

s1_avg_4clusters_s2_trends <- bind_cols(clusters4_s1_avg_spread, 
                                        s2_spread[, 2:ncol(s2_spread)])

s1_avg_4clusters_s2_trends <- merge(s1_avg_4clusters_s2_trends[, c("cluster_kmeans_4", "Show_Name")], 
                                     dct_df_avg, by = "Show_Name")

dct_s1_avg_4clusters_s2_trends <- s1_avg_4clusters_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s1_avg_4clusters_s2_trends_plot <- dct_s1_avg_4clusters_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_4, nrow = 4) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "#d8d8d8", 
                                        linetype = "dotted"), 
        strip.background = element_blank())

s1_avg_4kmeans_s2trends <- ggplotly(s1_avg_4clusters_s2_trends_plot) %>% 
  layout(title = "Season 1 with 4 K-Means Clusters & Season 2 Trends (C3 & LS Averages)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_avg_4kmeans_s2trends
```

```{r}
# GROUPINGS BY CLUSTER
by_cluster_4kmeans_avg <- plot_ly(dct_s1_avg_4clusters_s2_trends, 
        x = ~period, 
        y = ~dct_values, 
        color = ~Show_Name,
        yaxis = ~paste0('y', cluster_kmeans_4), 
        legendgroup = ~cluster_kmeans_4) %>% 
  add_lines() %>% 
  subplot(nrows = 4, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 4 K-Means Clusters & Season 2 Trends (C3 & LS Averages)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
by_cluster_4kmeans_avg
```

### 5 Clusters (K-Means)

```{r}
clusters5_s1_avg_spread<- assignments_s1_avg %>% 
  filter(k == 5) %>% 
  ungroup() %>% 
  select(.cluster) %>% 
  rename(cluster_kmeans_5 = .cluster) %>% 
  bind_cols(filter(dct_spread_avg, Season_num == 1)) 

clusters5_s1_avg <- merge(clusters5_s1_avg_spread[, c("cluster_kmeans_5", "Show_Name")], 
                          dct_df_avg, by = "Show_Name")

write.csv(clusters5_s1_avg, "kmeans_C3_LS_growth_avg_s1_5cl.csv")
```

```{r}
clusters5_s1_avg_plot <- clusters5_s1_avg %>% 
  filter(Season_num == 1) %>% 
  ggplot(aes(x = period, y = dct_values, 
             color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 5) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

s1_avg_5kmeans <- ggplotly(clusters5_s1_avg_plot) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 5 K-Means Clusters (C3 & LS Averages)", 
         autosize = FALSE, width = 550, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_avg_5kmeans
```

#### List Show Names within Clusters

```{r}
s1_avg_5clusters <- list(as.character(unique(clusters5_s1_avg[clusters5_s1_avg$cluster_kmeans_5 == 1,]$Show_Name)),
                         as.character(unique(clusters5_s1_avg[clusters5_s1_avg$cluster_kmeans_5 == 2,]$Show_Name)),
                         as.character(unique(clusters5_s1_avg[clusters5_s1_avg$cluster_kmeans_5 == 3,]$Show_Name)),
                         as.character(unique(clusters5_s1_avg[clusters5_s1_avg$cluster_kmeans_5 == 4,]$Show_Name)),
                         as.character(unique(clusters5_s1_avg[clusters5_s1_avg$cluster_kmeans_5 == 5,]$Show_Name)))
s1_avg_5clusters
```

```{r}
# S1 CLUSTERS & S2 TRENDS
s1_avg_5clusters_s2_trends <- bind_cols(clusters5_s1_avg_spread, 
                                        s2_spread[, 2:ncol(s2_spread)])

s1_avg_5clusters_s2_trends <- merge(s1_avg_5clusters_s2_trends[, c("cluster_kmeans_5", "Show_Name")], 
                                    dct_df_avg, by = "Show_Name")

dct_s1_avg_5clusters_s2_trends <- s1_avg_5clusters_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())

write.csv(dct_s1_avg_5clusters_s2_trends, "kmeans_C3_LS_growth_avg_s1_5cl_s2trends.csv")
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s1_avg_5clusters_s2_trends_plot <- dct_s1_avg_5clusters_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster_kmeans_5, nrow = 5) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "#d8d8d8", 
                                        linetype = "dotted"), 
        strip.background = element_blank())

s1_avg_5kmeans_s2trends <- ggplotly(s1_avg_5clusters_s2_trends_plot) %>% 
  layout(title = "Season 1 with 5 K-Means Clusters & Season 2 Trends (C3 & LS Averages)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
s1_avg_5kmeans_s2trends
```

```{r}
# GROUPINGS BY CLUSTER
by_cluster_5kmeans_avg <- plot_ly(dct_s1_avg_5clusters_s2_trends, 
        x = ~period, 
        y = ~dct_values, 
        color = ~Show_Name,
        yaxis = ~paste0('y', cluster_kmeans_5), 
        legendgroup = ~cluster_kmeans_5) %>% 
  add_lines() %>% 
  subplot(nrows = 5, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "Season 1 with 5 K-Means Clusters & Season 2 Trends (C3 & LS Averages)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))
by_cluster_5kmeans_avg
```

```{r}
# S1-S2 Trends Clustered on S1 Clusters
dct_spread_avg_cont <- read.csv("dct_spread_C3_LS_avg_growth_cont.csv") %>% select(-X)
dct_avg_cont <- read.csv("dct_C3_LS_avg_growth_cont.csv")

season1_kmeans5_clusters <- clusters5_s1_avg_spread %>% 
  select(Show_Name, cluster_kmeans_5) %>% 
  rename(s1_cluster = cluster_kmeans_5)

s1_clusters_cont_trends <- merge(season1_kmeans5_clusters, 
                                 dct_spread_avg_cont, by = "Show_Name")

s1_clusters_cont_trends <- merge(s1_clusters_cont_trends[, c("Show_Name", "s1_cluster")], 
                                 dct_avg_cont, by = "Show_Name") %>% select(-X)

write.csv(s1_clusters_cont_trends, "kmeans_C3_LS_growth_avg_s1_5cl_cont_trends.csv") 
```

```{r}
# Plot for Continuous Trends Clustered on S1 Clusters
s1_clusters_cont_trends_plot <- plot_ly(s1_clusters_cont_trends, 
        x = ~period, 
        y = ~dct_values, 
        color = ~Show_Name,
        yaxis = ~paste0('y', s1_cluster), 
        legendgroup = ~s1_cluster) %>% 
  add_lines() %>% 
  subplot(nrows = 5, shareX = TRUE) %>% 
  layout(showlegend = TRUE, 
         title = "S1-S2 Clustered on S1 Clusters (C3 + LS Growth Averages)", 
         autosize = FALSE, width = 650, height = 800, 
         margin = list(l = 50, 
                       r = 50, 
                       b = 50, 
                       t = 125))

s1_clusters_cont_trends_plot
```


# Diagnostics
 
```{r}
# create distance matrices for clusters
kmeans_s1_4cl_d <- dist(clusters4_s1_spread[, 5:204])
kmeans_s1_5cl_d <- dist(clusters5_s1_spread[, 5:204])
kmeans_s1_diff_3cl_d <- dist(clusters3_s1_diff_spread[, 5:104])
kmeans_s1_diff_4cl_d <- dist(clusters4_s1_diff_spread[, 5:104])
kmeans_s1_diff_5cl_d <- dist(clusters5_s1_diff_spread[, 5:104])
kmeans_s1_avg_4cl_d <- dist(clusters4_s1_avg_spread[, 5:104])
kmeans_s1_avg_5cl_d <- dist(clusters5_s1_avg_spread[, 5:104])

# diagnostics
diagnostics_kmeans_C3_LS_growth_s1_4cl <- cluster.stats(kmeans_s1_4cl_d, as.numeric(clusters4_s1_spread$cluster_kmeans_4))
diagnostics_kmeans_C3_LS_growth_s1_5cl <- cluster.stats(kmeans_s1_5cl_d, as.numeric(clusters5_s1_spread$cluster_kmeans_5))
diagnostics_kmeans_C3_LS_growth_diff_s1_3cl <- cluster.stats(kmeans_s1_diff_3cl_d, as.numeric(clusters3_s1_diff_spread$cluster_kmeans_3))
diagnostics_kmeans_C3_LS_growth_diff_s1_4cl <- cluster.stats(kmeans_s1_diff_4cl_d, as.numeric(clusters4_s1_diff_spread$cluster_kmeans_4))
diagnostics_kmeans_C3_LS_growth_diff_s1_5cl <- cluster.stats(kmeans_s1_diff_5cl_d, as.numeric(clusters5_s1_diff_spread$cluster_kmeans_5))
diagnostics_kmeans_C3_LS_growth_avg_s1_4cl <- cluster.stats(kmeans_s1_avg_4cl_d, as.numeric(clusters4_s1_avg_spread$cluster_kmeans_4))
diagnostics_kmeans_C3_LS_growth_avg_s1_5cl <- cluster.stats(kmeans_s1_avg_5cl_d, as.numeric(clusters5_s1_avg_spread$cluster_kmeans_5))

# gather diagnostic names and list all diagnostics objects
d_names <- ls()[grep("diagnostics", ls())]
d_list <- mget(ls()[grep("diagnostics", ls())])

# generate df with statsitics of interest for comparison
diagnostic_df <- as.data.frame(NA)

for (n in 1:length(d_names)){
  diagnostic_df[n, 1] <- paste(d_names[n])
  diagnostic_df[n, 2] <- d_list[[n]]["average.between"]
  diagnostic_df[n, 3] <- d_list[[n]]["average.within"]
  diagnostic_df[n, 4] <- d_list[[n]]["wb.ratio"]
  diagnostic_df[n, 5] <- d_list[[n]]["widestgap"]
  diagnostic_df[n, 6] <- d_list[[n]]["dunn2"]
  diagnostic_df[n, 7] <- d_list[[n]]["avg.silwidth"]
  diagnostic_df[n, 8] <- d_list[[n]]["within.cluster.ss"]
  diagnostic_df[n, 9] <- d_list[[n]]["cluster.number"]
}

# add information for decision making
colnames(diagnostic_df)[1] <- "name"

diagnostic_df$name <- sub("diagnostics_", "", diagnostic_df$name)

diagnostic_df$algorithm <- ifelse(grepl("kmeans", diagnostic_df$name) == 1, "kmeans", 
                                  ifelse(grepl("kshape", diagnostic_df$name) == 1, "kshape", 
                                         ifelse(grepl("PCA", diagnostic_df$name) == 1, "PCA", 
                                                ifelse(grepl("tadpole", diagnostic_df$name) == 1, "TADpole", 
                                                       ifelse(grepl("dtw", diagnostic_df$name) == 1, "DTW", 0)))))

diagnostic_df$season <- ifelse(grepl("s1", diagnostic_df$name) == 1, "s1", 
                               ifelse(grepl("s2", diagnostic_df$name) == 1, "s2",
                                      ifelse(grepl("sep", diagnostic_df$name) == 1, "sep",
                                             ifelse(grepl("cont", diagnostic_df$name) == 1, "cont", 0))))

diagnostic_df$stream <- ifelse(grepl("C3_LS", diagnostic_df$name) == 1, "C3+LS",
                                             ifelse(grepl("LS", diagnostic_df$name) == 1, "LS",
                                                    ifelse(grepl("C3", diagnostic_df$name) == 1, "C3", 0)))

diagnostic_df$data <- ifelse(grepl("raw_diff", diagnostic_df$name) == 1, "raw diff",
                             ifelse(grepl("raw_avg", diagnostic_df$name) == 1, "raw avg",
                                    ifelse(grepl("growth_diff", diagnostic_df$name) == 1, "growth diff",
                                           ifelse(grepl("growth_avg", diagnostic_df$name) == 1, "growth avg", 
                                                  ifelse(grepl("raw_growth", diagnostic_df$name) == 1, "raw+growth",
                                                         ifelse(grepl("growth", diagnostic_df$name) == 1, "growth",
                                                                ifelse(grepl("raw", diagnostic_df$name) == 1, "raw",0)))))))
```

```{r}
# write table
write.csv(diagnostic_df, "diagnostics_kmeans_C3_LS_growth.csv")
```
