---
title: "CENT S1-S2 TADpole Clustering on C3 Impressions"
output:
  html_notebook: default
  html_document: default
---

```{r}
##################################################################################
# inputs: dct_C3_raw.csv, dct_spread_C3_raw.csv,
#         dct_C3_raw_cont.csv, dct_spread_C3_raw_cont.csv
#
# purpose: tadpole clustering (3 and 5 clusters for S1, S2 (3 and 4 clusters),
#          S1 & S2 normalized together, and S1-S2)
##################################################################################
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r}
library(plyr)
library(dplyr)
library(dtwclust)
library(ggplot2)
library(tidyr)
library(plotly)
library(fpc)
```

# Season 1 Clustering

## TADpole Clustering, 5 Clusters

```{r}
#read and filter data
dct_spread <- read.csv("dct_spread_C3_raw.csv")
dct_df <- read.csv("dct_C3_raw.csv")

dtw_df_s1 <- dct_spread %>% 
  filter(Season_num == 1) %>%
  select(-X, -Network, -Season_num, -Show_Name)
```

```{r}
#Run TadPole clustering. arguments adjusted a-posteriori based on visualizations
set.seed(12)
tadpole_clust5_s1 <- tsclust(dtw_df_s1, type = "tadpole", k = 5L, 
                             control = tadpole_control(dc = 2, window.size = 25))

#Attach clusters to DCT data
tadpole_clust5_s1_df <- dct_spread %>% 
  filter(Season_num == 1) %>% 
  select(-Season_num)

tadpole_clust5_s1_df$cluster <- tadpole_clust5_s1@cluster  

#long data format
tadpole5_s1_long <- gather(tadpole_clust5_s1_df, key = period, value = dct_values ,X1:X100) %>% 
  select(-X)
tadpole5_s1_long$period <- as.numeric(sub("X", "", tadpole5_s1_long$period))
tadpole5_s1_long$period <- as.numeric(tadpole5_s1_long$period)

#plot
tadpole5_s1_plot <- tadpole5_s1_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3)

ggplotly(tadpole5_s1_plot) %>% 
  layout(title = "Season 1 with 5 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_s1_5clusters <- list(as.character(unique(tadpole_clust5_s1_df[tadpole_clust5_s1_df$cluster == 1,]$Show_Name)),
                             as.character(unique(tadpole_clust5_s1_df[tadpole_clust5_s1_df$cluster == 2,]$Show_Name)),
                             as.character(unique(tadpole_clust5_s1_df[tadpole_clust5_s1_df$cluster == 3,]$Show_Name)),
                             as.character(unique(tadpole_clust5_s1_df[tadpole_clust5_s1_df$cluster == 4,]$Show_Name)),
                             as.character(unique(tadpole_clust5_s1_df[tadpole_clust5_s1_df$cluster == 5,]$Show_Name)))
tadpole_s1_5clusters
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s2_spread <- dct_spread %>% 
  filter(Season_num == 2) %>%
  ungroup() %>%
  select(-X, -Network, -Season_num)

s2_spread_newcols <- c(paste("X", 101:200, sep = ""))
colnames(s2_spread)[2:ncol(s2_spread)] <- c(s2_spread_newcols)

s1_5clusters_tadpole_s2_trends <- bind_cols(tadpole_clust5_s1_df, 
                                            s2_spread[, 2:ncol(s2_spread)])

s1_5clusters_tadpole_s2_trends <- merge(s1_5clusters_tadpole_s2_trends[, c("cluster", 
                                                                           "Show_Name")], 
                                        dct_df, by = "Show_Name")

dct_s1_5clusters_tadpole_s2_trends <- s1_5clusters_tadpole_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())

s1_5clusters_tadpole_s2_trends_plot <- dct_s1_5clusters_tadpole_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(s1_5clusters_tadpole_s2_trends_plot) %>% 
  layout(title = "Season 1 with 5 TADpole Clusters & Season 2 Trends (C3)", 
         margin = list(t = 150))
```

## TADpole Clustering, 3 Clusters

```{r}
set.seed(12)
tadpole_clust3_s1 <- tsclust(dtw_df_s1, type = "tadpole", k = 3L, 
                             control = tadpole_control(dc = 2, window.size = 25))

tadpole_clust3_s1_df<- dct_spread %>% 
  filter(Season_num == 1) %>% 
  select(-Season_num)

tadpole_clust3_s1_df$cluster <- tadpole_clust3_s1@cluster  

tadpole3_s1_long <- gather(tadpole_clust3_s1_df, key = period, value = dct_values ,X1:X100) %>% 
  select(-X)
tadpole3_s1_long$period <- as.numeric(sub("X", "", tadpole3_s1_long$period))
tadpole3_s1_long$period <- as.numeric(tadpole3_s1_long$period)

tadpole3_s1_plot <- tadpole3_s1_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3)

ggplotly(tadpole3_s1_plot) %>% 
  layout(title = "Season 1 with 3 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_s1_3clusters <- list(as.character(unique(tadpole_clust3_s1_df[tadpole_clust3_s1_df$cluster == 1,]$Show_Name)),
                             as.character(unique(tadpole_clust3_s1_df[tadpole_clust3_s1_df$cluster == 2,]$Show_Name)),
                             as.character(unique(tadpole_clust3_s1_df[tadpole_clust3_s1_df$cluster == 3,]$Show_Name)))
tadpole_s1_3clusters
```

```{r}
# PLOT FOR S1 CLUSTERS & S2 TRENDS
s1_3clusters_tadpole_s2_trends <- bind_cols(tadpole_clust3_s1_df, 
                                            s2_spread[, 2:ncol(s2_spread)])

s1_3clusters_tadpole_s2_trends <- merge(s1_3clusters_tadpole_s2_trends[, c("cluster", 
                                                                           "Show_Name")], 
                                        dct_df, by = "Show_Name")

dct_s1_3clusters_tadpole_s2_trends <- s1_3clusters_tadpole_s2_trends %>% 
  filter(Season_num == 1 | Season_num == 2) %>% 
  group_by(Network, Show_Name) %>% 
  mutate(period = row_number())

s1_3clusters_tadpole_s2_trends_plot <- dct_s1_3clusters_tadpole_s2_trends %>%
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3) + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank())

ggplotly(s1_3clusters_tadpole_s2_trends_plot) %>% 
  layout(title = "Season 1 with 3 TADpole Clusters & Season 2 Trends (C3)", 
         margin = list(t = 150))
```


-----------------------------------------------------------------------------------------------------------
-----------------------------------------------------------------------------------------------------------


# Season 2 Clustering

## TADpole Clustering, 4 Clusters
```{r}
dtw_df_s2 <- dct_spread %>% 
  filter(Season_num == 2) %>%
  select(-X, -Network, -Season_num, -Show_Name)
```

```{r}
set.seed(12)
tadpole_clust4_s2 <- tsclust(dtw_df_s2, type = "tadpole", k = 4L, 
                             control = tadpole_control(dc = 10, window.size = 3))

tadpole_clust4_s2_df<- dct_spread %>% 
  filter(Season_num == 2) %>% 
  select(-Season_num)

tadpole_clust4_s2_df$cluster <- tadpole_clust4_s2@cluster  

tadpole4_s2_long <- gather(tadpole_clust4_s2_df, key = period, value = dct_values ,X1:X100) %>% 
  select(-X)
tadpole4_s2_long$period <- as.numeric(sub("X", "", tadpole4_s2_long$period ))
tadpole4_s2_long$period <- as.numeric(tadpole4_s2_long$period)

tadpole4_s2_plot <- tadpole4_s2_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster)

ggplotly(tadpole4_s2_plot) %>% 
  layout(title = "Season 2 with 4 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_s2_4clusters <- list(as.character(unique(tadpole_clust4_s2_df[tadpole_clust4_s2_df$cluster == 1,]$Show_Name)),
                             as.character(unique(tadpole_clust4_s2_df[tadpole_clust4_s2_df$cluster == 2,]$Show_Name)),
                             as.character(unique(tadpole_clust4_s2_df[tadpole_clust4_s2_df$cluster == 3,]$Show_Name)),
                             as.character(unique(tadpole_clust4_s2_df[tadpole_clust4_s2_df$cluster == 4,]$Show_Name)))
tadpole_s2_4clusters
```

## TADpole Clustering, 3 Clusters

```{r}
set.seed(12)
tadpole_clust3_s2 <- tsclust(dtw_df_s2, type = "tadpole", k = 3L, 
                             control = tadpole_control(dc = 2, window.size = 25))

tadpole_clust3_s2_df<- dct_spread %>% 
  filter(Season_num == 2) %>% 
  select(-Season_num)

tadpole_clust3_s2_df$cluster <- tadpole_clust3_s2@cluster  

tadpole3_s2_long <- gather(tadpole_clust3_s2_df, key = period, value = dct_values ,X1:X100) %>% 
  select(-X)
tadpole3_s2_long$period <- as.numeric(sub("X", "", tadpole3_s2_long$period ))
tadpole3_s2_long$period <- as.numeric(tadpole3_s2_long$period)

tadpole3_s2_plot <- tadpole3_s2_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3)

ggplotly(tadpole3_s2_plot) %>% 
  layout(title = "Season 2 with 3 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_s2_3clusters <- list(as.character(unique(tadpole_clust3_s2_df[tadpole_clust3_s2_df$cluster == 1,]$Show_Name)),
                             as.character(unique(tadpole_clust3_s2_df[tadpole_clust3_s2_df$cluster == 2,]$Show_Name)),
                             as.character(unique(tadpole_clust3_s2_df[tadpole_clust3_s2_df$cluster == 3,]$Show_Name)))
tadpole_s2_3clusters
```


-----------------------------------------------------------------------------------------------------------
-----------------------------------------------------------------------------------------------------------


# S1-S2 Continuous Clustering

## TADpole Clustering, 5 Clusters

```{r}
dct_cont <- read.csv("dct_C3_raw_cont.csv")
dct_spread_cont <- read.csv("dct_spread_C3_raw_cont.csv")
dtw_df_cont <- dct_spread_cont %>%
  select(-X, -Network, -Show_Name)
```

```{r}
set.seed(12)
tadpole_clust5_cont <- tsclust(dtw_df_cont, type = "tadpole", k = 5L, 
                               control = tadpole_control(dc = 50, window.size = 5))

tadpole_clust5_cont_df<- dct_spread_cont

tadpole_clust5_cont_df$cluster <- tadpole_clust5_cont@cluster  

tadpole5_cont_long <- gather(tadpole_clust5_cont_df, key = period, value = dct_values ,X1:X100) %>% 
  select(-X)
tadpole5_cont_long$period <- as.numeric(sub("X", "", tadpole5_cont_long$period ))
tadpole5_cont_long$period <- as.numeric(tadpole5_cont_long$period)

tadpole5_cont_plot <- tadpole5_cont_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster)

ggplotly(tadpole5_cont_plot) %>% 
  layout(title = "S1-S2 (Continuous) with 5 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_cont_5clusters <- list(as.character(unique(tadpole_clust5_cont_df[tadpole_clust5_cont_df$cluster == 1,]$Show_Name)),
                               as.character(unique(tadpole_clust5_cont_df[tadpole_clust5_cont_df$cluster == 2,]$Show_Name)),
                               as.character(unique(tadpole_clust5_cont_df[tadpole_clust5_cont_df$cluster == 3,]$Show_Name)),
                               as.character(unique(tadpole_clust5_cont_df[tadpole_clust5_cont_df$cluster == 4,]$Show_Name)),
                               as.character(unique(tadpole_clust5_cont_df[tadpole_clust5_cont_df$cluster == 5,]$Show_Name)))
tadpole_cont_5clusters
```

## TADpole Clustering, 3 Clusters

```{r}
set.seed(12)
tadpole_clust3_cont <- tsclust(dtw_df_cont, type = "tadpole", k = 3L, 
                               control = tadpole_control(dc = 10, window.size = 3))

tadpole_clust3_cont_df<- dct_spread_cont

tadpole_clust3_cont_df$cluster <- tadpole_clust3_cont@cluster  

tadpole3_cont_long <- gather(tadpole_clust3_cont_df, key = period, value = dct_values ,X1:X100) %>% 
  select(-X)
tadpole3_cont_long$period <- as.numeric(sub("X", "", tadpole3_cont_long$period ))
tadpole3_cont_long$period <- as.numeric(tadpole3_cont_long$period)

tadpole3_cont_plot <- tadpole3_cont_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3)

ggplotly(tadpole3_cont_plot) %>% 
  layout(title = "S1-S2 (Continuous) with 3 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_cont_3clusters <- list(as.character(unique(tadpole_clust3_cont_df[tadpole_clust3_cont_df$cluster == 1,]$Show_Name)),
                               as.character(unique(tadpole_clust3_cont_df[tadpole_clust3_cont_df$cluster == 2,]$Show_Name)),
                               as.character(unique(tadpole_clust3_cont_df[tadpole_clust3_cont_df$cluster == 3,]$Show_Name)))
tadpole_cont_3clusters
```


-----------------------------------------------------------------------------------------------------------
-----------------------------------------------------------------------------------------------------------


# S1-S2 Non-Continuous Clustering

## TADpole Clustering, 5 Clusters

```{r}
temp1 <- filter(dct_spread, Season_num == 1)
temp2 <- filter(dct_spread, Season_num == 2)
temp2_newcols <- c(paste("X", 101:200, sep = ""))
colnames(temp2)[5:ncol(temp2)] <- c(temp2_newcols)

tadpole_spread_s1_s2 <- bind_cols(temp1, temp2[, 5:ncol(temp2)])
rm(temp1, temp2, temp2_newcols)

tadpole_s1_s2 <- tadpole_spread_s1_s2 %>%
  select(-X, -Network, -Season_num, -Show_Name)
```

```{r}
set.seed(12)
tadpole_clust5_s1_s2 <- tsclust(tadpole_s1_s2, type = "tadpole", k = 5L, 
                                control = tadpole_control(dc = 50, window.size = 2))

tadpole_clust5_s1_s2_df<- tadpole_spread_s1_s2

tadpole_clust5_s1_s2_df$cluster <- tadpole_clust5_s1_s2@cluster  

tadpole5_s1_s2_long <- gather(tadpole_clust5_s1_s2_df, key = period, value = dct_values ,X1:X200) %>% 
  select(-X)
tadpole5_s1_s2_long$period <- as.numeric(sub("X", "", tadpole5_s1_s2_long$period ))
tadpole5_s1_s2_long$period <- as.numeric(tadpole5_s1_s2_long$period)

tadpole5_s1_s2_plot <- tadpole5_s1_s2_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3)

ggplotly(tadpole5_s1_s2_plot) %>% 
  layout(title = "S1-S2 (Non-Continuous) with 5 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_s1_s2_5clusters <- list(as.character(unique(tadpole_clust5_s1_s2_df[tadpole_clust5_s1_s2_df$cluster == 1,]$Show_Name)),
                                as.character(unique(tadpole_clust5_s1_s2_df[tadpole_clust5_s1_s2_df$cluster == 2,]$Show_Name)),
                                as.character(unique(tadpole_clust5_s1_s2_df[tadpole_clust5_s1_s2_df$cluster == 3,]$Show_Name)),
                                as.character(unique(tadpole_clust5_s1_s2_df[tadpole_clust5_s1_s2_df$cluster == 4,]$Show_Name)),
                                as.character(unique(tadpole_clust5_s1_s2_df[tadpole_clust5_s1_s2_df$cluster == 5,]$Show_Name)))
tadpole_s1_s2_5clusters
```

## TADpole Clustering, 3 Clusters

```{r}
set.seed(12)
tadpole_clust3_s1_s2 <- tsclust(tadpole_s1_s2, type = "tadpole", k = 3L, 
                               control = tadpole_control(dc = 25, window.size = 3))

tadpole_clust3_s1_s2_df<- tadpole_spread_s1_s2

tadpole_clust3_s1_s2_df$cluster <- tadpole_clust3_s1_s2@cluster  

tadpole3_s1_s2_long <- gather(tadpole_clust3_s1_s2_df, key = period, value = dct_values ,X1:X200) %>% 
  select(-X)
tadpole3_s1_s2_long$period <- as.numeric(sub("X", "", tadpole3_s1_s2_long$period ))
tadpole3_s1_s2_long$period <- as.numeric(tadpole3_s1_s2_long$period)

tadpole3_s1_s2_plot <- tadpole3_s1_s2_long %>% 
  ggplot(aes(x = period, y = dct_values, color = Show_Name)) + 
  geom_line() + 
  facet_wrap(~ cluster, nrow = 3)

ggplotly(tadpole3_s1_s2_plot) %>% 
  layout(title = "S1-S2 (Non-Continuous) with 3 TADpole Clusters (C3)", 
         margin = list(t = 150))
```

### Shows in Each Cluster

```{r}
tadpole_s1_s1_3clusters <- list(as.character(unique(tadpole_clust3_s1_s2_df[tadpole_clust3_s1_s2_df$cluster == 1,]$Show_Name)),
                                as.character(unique(tadpole_clust3_s1_s2_df[tadpole_clust3_s1_s2_df$cluster == 2,]$Show_Name)),
                                as.character(unique(tadpole_clust3_s1_s2_df[tadpole_clust3_s1_s2_df$cluster == 3,]$Show_Name)))
tadpole_s1_s1_3clusters
```

# Diagnostics
 
```{r}
# create distance matrices for clusters
tadpole_s1_5cl_d <- dist(tadpole_clust5_s1_df[, 4:103])
tadpole_s1_3cl_d <- dist(tadpole_clust3_s1_df[, 4:103])
tadpole_s2_4cl_d <- dist(tadpole_clust4_s2_df[, 4:103])
tadpole_s2_3cl_d <- dist(tadpole_clust3_s2_df[, 4:103])
tadpole_cont_5cl_d <- dist(tadpole_clust5_cont_df[, 4:103])
tadpole_cont_3cl_d <- dist(tadpole_clust3_cont_df[, 4:103])
tadpole_sep_5cl_d <- dist(tadpole_clust5_s1_s2_df[, 5:204])
tadpole_sep_3cl_d <- dist(tadpole_clust3_s1_s2_df[, 5:204])

# diagnostics
diagnostics_tadpole_C3_raw_s1_5cl <- cluster.stats(tadpole_s1_5cl_d, as.numeric(tadpole_clust5_s1_df$cluster))
diagnostics_tadpole_C3_raw_s1_3cl <- cluster.stats(tadpole_s1_3cl_d, as.numeric(tadpole_clust3_s1_df$cluster))
diagnostics_tadpole_C3_raw_s2_4cl <- cluster.stats(tadpole_s2_4cl_d, as.numeric(tadpole_clust4_s2_df$cluster))
diagnostics_tadpole_C3_raw_s2_3cl <- cluster.stats(tadpole_s2_3cl_d, as.numeric(tadpole_clust3_s2_df$cluster))
diagnostics_tadpole_C3_raw_cont_5cl <- cluster.stats(tadpole_cont_5cl_d, as.numeric(tadpole_clust5_cont_df$cluster))
diagnostics_tadpole_C3_raw_cont_3cl <- cluster.stats(tadpole_cont_3cl_d, as.numeric(tadpole_clust3_cont_df$cluster))
diagnostics_tadpole_C3_raw_sep_5cl <- cluster.stats(tadpole_sep_5cl_d, as.numeric(tadpole_clust5_s1_s2_df$cluster))
diagnostics_tadpole_C3_raw_sep_3cl <- cluster.stats(tadpole_sep_3cl_d, as.numeric(tadpole_clust3_s1_s2_df$cluster))

# gather diagnostic names and list all diagnostics objects
d_names <- ls()[grep("diagnostics", ls())]
d_list <- mget(ls()[grep("diagnostics", ls())])

# generate df with statsitics of interest for comparison
diagnostic_df <- as.data.frame(NA)

for (n in 1:length(d_names)){
  diagnostic_df[n, 1] <- paste(d_names[n])
  diagnostic_df[n, 2] <- d_list[[n]]["average.between"]
  diagnostic_df[n, 3] <- d_list[[n]]["average.within"]
  diagnostic_df[n, 4] <- d_list[[n]]["wb.ratio"]
  diagnostic_df[n, 5] <- d_list[[n]]["widestgap"]
  diagnostic_df[n, 6] <- d_list[[n]]["dunn2"]
  diagnostic_df[n, 7] <- d_list[[n]]["avg.silwidth"]
  diagnostic_df[n, 8] <- d_list[[n]]["within.cluster.ss"]
  diagnostic_df[n, 9] <- d_list[[n]]["cluster.number"]
}

# add information for decision making
colnames(diagnostic_df)[1] <- "name"

diagnostic_df$name <- sub("diagnostics_", "", diagnostic_df$name)

diagnostic_df$algorithm <- ifelse(grepl("kmeans", diagnostic_df$name) == 1, "kmeans", 
                                  ifelse(grepl("kshape", diagnostic_df$name) == 1, "kshape", 
                                         ifelse(grepl("PCA", diagnostic_df$name) == 1, "PCA", 
                                                ifelse(grepl("tadpole", diagnostic_df$name) == 1, "TADpole", 
                                                       ifelse(grepl("dtw", diagnostic_df$name) == 1, "DTW", 0)))))

diagnostic_df$season <- ifelse(grepl("s1", diagnostic_df$name) == 1, "s1", 
                               ifelse(grepl("s2", diagnostic_df$name) == 1, "s2",
                                      ifelse(grepl("sep", diagnostic_df$name) == 1, "sep",
                                             ifelse(grepl("cont", diagnostic_df$name) == 1, "cont", 0))))

diagnostic_df$stream <- ifelse(grepl("C3_LS", diagnostic_df$name) == 1, "C3+LS",
                                             ifelse(grepl("LS", diagnostic_df$name) == 1, "LS",
                                                    ifelse(grepl("C3", diagnostic_df$name) == 1, "C3", 0)))

diagnostic_df$data <- ifelse(grepl("raw_diff", diagnostic_df$name) == 1, "raw diff",
                             ifelse(grepl("raw_avg", diagnostic_df$name) == 1, "raw avg",
                                    ifelse(grepl("growth_diff", diagnostic_df$name) == 1, "growth diff",
                                           ifelse(grepl("growth_avg", diagnostic_df$name) == 1, "growth avg", 
                                                  ifelse(grepl("raw_growth", diagnostic_df$name) == 1, "raw+growth",
                                                         ifelse(grepl("growth", diagnostic_df$name) == 1, "growth",
                                                                ifelse(grepl("raw", diagnostic_df$name) == 1, "raw",0)))))))
```

```{r}
# write table
write.csv(diagnostic_df, "diagnostics_tadpole_C3_raw.csv")
```