---
title: "Exploratory Plots for Raw LS Impressions"
output:
  html_notebook: default
  html_document: default
---

```{r}
##################################################################################
# inputs: CENT_showlevel.csv
#
# purpose: Exploratory plots for raw, growth, and 1st episode rebase trends,
#          non-normalized LS impressions
##################################################################################
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, error = FALSE, echo = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
library(plotly)
library(scales)
```

# Raw LS Impressions

Read data
```{r}
df <- read.csv("CENT_showlevel.csv")
df <- select(df, -X)
```

Define ggplot theme
```{r}
my_theme <-  theme(panel.background = element_blank(), 
                   panel.grid.major = element_line(color = "#d8d8d8", linetype = "dotted"), 
                   panel.grid.major.x = element_blank(), 
                   plot.title = element_text(hjust = 0.5),
                   axis.title.x = element_blank(), 
                   axis.title.y = element_blank(),
                   axis.line.y = element_blank(),
                   axis.ticks.y = element_blank(),
                   axis.line.x = element_line(color = "#d8d8d8", linetype = "dashed"),
                   strip.background = element_blank())
```

Descriptive measures
```{r}
# cases per network
table(df$Network)

# how many shows
length(unique(df$Show_Name))
```

Episode count of shows 
```{r}
ggplotly(ggplot(df %>% filter(Season_num < 3 & Season_num != 0) %>% 
                  group_by(Network, Show_Name, Season_num) %>% 
                  summarise(episodes = max(Episode_num))) + 
           geom_histogram(aes(x= episodes), binwidth = 1) + 
           my_theme, 
           width = 1000, 
           height = 750)
```

```{r}
length(which((df %>% filter(Season_num < 3 & Season_num != 0) %>% 
                group_by(Network, Show_Name, Season_num) %>%
                summarise(episodes = max(Episode_num)))$episodes > 14)) 
```

# S1 to S2

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                  group_by(Season_num) %>%
                  summarise(LS = mean(LS_Impressions))) +
           geom_line(aes(x = Season_num, y = LS)) +
           geom_line(data = (df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                  group_by(Network, Season_num) %>%
                  summarise(LS = mean(LS_Impressions))), 
                  aes(x = Season_num, y = LS, color = Network)) + 
           my_theme + ggtitle("S1-S2 Trends for All Networks (Average LS Impressions)"))
```

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_smooth(aes(x = Season_num, y = LS_Impressions, color = Network), 
                       se = F, method = "lm") +
           stat_smooth(aes(x = Season_num, y = LS_Impressions, color = Show_Name), 
                       geom = "line", se = F, method = "lm", alpha = 0.4) +
           geom_smooth(aes(x = Season_num, y = LS_Impressions), 
                       color = "black", se = F, method = "lm", linetype = "dashed") + 
           my_theme + ggtitle("S1-S2 Linear Trends for All Shows (LS Impressions)"),
           width = 1000, 
           height = 750)
```

# LS Impressions

Shows

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_line(aes(x = Episode_num, y = LS_Impressions, color = Show_Name), 
                     se = F, method = "lm", alpha = 0.4, formula = y ~ 0 + x) +
           geom_smooth(aes(x = Episode_num, y = LS_Impressions), 
                       color = "black", se = F, method = lm, linetype = "dashed") +
           facet_grid(Network ~ Season_num ) +
           my_theme +
           theme(legend.position = "none") +
           ggtitle("S1-S2 Trends for All Shows (LS Impressions)"), 
           width = 750,
           height = 1000)
```

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           stat_smooth(aes(x = Episode_num, y = LS_Impressions, color = Show_Name), 
                       geom = "line", se = F, method = "lm", alpha = 0.5) + 
           stat_smooth(aes(x = Episode_num, y = LS_Impressions), 
                       geom = "line", color = "black", se = F, method = "lm", 
                       linetype = "dashed", alpha = 0.7) + 
           facet_grid(Network ~ Season_num ) +
           my_theme +
           theme(legend.position = "none") +
           ggtitle("S1-S2 Linear Trends for All Shows (LS Impressions)"),
           width = 750,
           height = 1000)
```

S1-S2 Trends for All Networks (LS Impressions, Episode Average)
```{R}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                  group_by(Network, Season_num, Episode_num) %>% 
                  summarise(avg_imp = mean(LS_Impressions))) + 
           geom_point(aes(x = Episode_num, y = avg_imp, color = Network)) +
           geom_line(aes(x = Episode_num, y = avg_imp, color = Network)) +
           geom_line(data = (df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                               group_by(Season_num, Episode_num) %>% 
                               summarise(avg_imp = mean(LS_Impressions))), 
                     aes(x = Episode_num, y = avg_imp), 
                     color = "black", linetype = "dashed") + 
           scale_y_continuous(labels = comma) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Trends for All Networks (LS Impressions, Episode Average)") +
           my_theme,
           width = 1000,
           height = 750)
```

S1-S2 Linear Trends for All Networks (LS Impressions)
```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_jitter(aes(x = Episode_num, y = LS_Impressions, 
                           color = Network), alpha = 0.35) + 
           geom_smooth(aes(x = Episode_num, y = LS_Impressions, 
                           color = Network), se = F, method = lm) + 
           geom_smooth(aes(x = Episode_num, y = LS_Impressions), 
                       color = "black", se = F, method = lm, linetype = "dashed") + 
           scale_y_continuous(labels = comma) +
           coord_cartesian(ylim = c(0, 750000)) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Linear Trends for All Networks (LS Impressions)") +
           my_theme,
           width = 1000,
           height = 750)
```

S1-S2 Smooth Trends for All Networks (LS Impressions)
```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_jitter(aes(x = Episode_num, y = LS_Impressions, 
                           color = Network), alpha = 0.35) + 
           geom_smooth(aes(x = Episode_num, y = LS_Impressions, 
                           color = Network), se = F) +
           geom_smooth(aes(x = Episode_num, y = LS_Impressions), 
                       color = "black", se = F, linetype = "dashed") +
           scale_y_continuous(labels = comma) +
           coord_cartesian(ylim = c(0, 750000)) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Smooth Trends for All Networks (LS Impressions)") +
           my_theme,
           width = 1000,
           heght = 750)
```

# Growth

Shows

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_line(aes(x = Episode_num, y = LS_Growth, color = Show_Name), 
                     se = F, alpha = 0.4) + 
           stat_smooth(aes(x = Episode_num, y = LS_Growth), 
                       geom = "line", color = "black", se = F, method = "lm", 
                       linetype = "dashed", alpha = 0.7) +
           facet_grid(Network ~ Season_num ) +
           my_theme +
           theme(legend.position = "none") +
           ggtitle("S1-S2 Trends for All Shows (LS Growth)"),
           width = 750,
           height = 1000)
```

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           stat_smooth(aes(x = Episode_num, y = LS_Growth, color = Show_Name), 
                       geom = "line", se = F, method = "lm", alpha = 0.5) +
           stat_smooth(aes(x = Episode_num, y = LS_Growth), 
                       geom = "line", color = "black", se = F, method = "lm", 
                       linetype = "dashed", alpha = 0.7) +
           facet_grid(Network ~ Season_num ) +
           my_theme +
           theme(legend.position = "none") +
           ggtitle("S1-S2 Linear Trends for All Shows (LS Growth)"),
           width = 750,
           height = 1000)

```

S1-S2 Trends for all Networks (LS Growth, Episode Average)
```{R}
ggplotly(ggplot(a <- df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                  group_by(Network, Season_num, Episode_num) %>% 
                  summarise(avg_growth = mean(LS_Growth, na.rm = T))) + 
           geom_point(aes(x = Episode_num, y = avg_growth, color = Network)) +
           geom_line(aes(x = Episode_num, y = avg_growth, color = Network)) +
           geom_line(data = (df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                               group_by(Season_num, Episode_num) %>% 
                               summarise(avg_growth = mean(LS_Growth, na.rm = T))), 
                     aes(x = Episode_num, y = avg_growth), color = "black", linetype = "dashed") + 
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Trends for all Networks (LS Growth, Episode Average)") +
           my_theme,
           width = 1000,
           height = 750)
```

S1-S2 Linear Trends for All Networks (LS Growth)
```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_jitter(aes(x = Episode_num, y = LS_Growth, color = Network), alpha = 0.35) +
           geom_smooth(aes(x = Episode_num, y = LS_Growth, color = Network), 
                       se = F, method = lm) +
           geom_smooth(aes(x = Episode_num, y = LS_Growth), 
                       color = "black", se = F, method = lm, linetype = "dashed") + 
           coord_cartesian(ylim = c(0.5, 1.5)) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Linear Trends for All Networks (LS Growth)") +
           my_theme,
           width = 1000,
           height = 750)
```

S1-S2 Smooth Trends for All Networks (LS Growth)
```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_jitter(aes(x = Episode_num, y = LS_Growth, 
                           color = Network), alpha = 0.35) + 
           geom_smooth(aes(x = Episode_num, y = LS_Growth, 
                           color = Network), se = F) + 
           geom_smooth(aes(x = Episode_num, y = LS_Growth), 
                       color = "black", se = F,linetype = "dashed") + 
           coord_cartesian(ylim = c(0.5, 1.5)) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Smooth Trends for All Networks (LS Growth)") +
           my_theme,
           width = 1000,
           height = 750)
```

# Rebase

Shows

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_line(aes(x = Episode_num, y = LS_Rebase, color = Show_Name), 
                     se = F, alpha = 0.4) + 
           stat_smooth(aes(x = Episode_num, y = LS_Rebase), 
                       geom = "line", color = "black", se = F, 
                       method = "lm", linetype = "dashed", alpha = 0.7) +
           facet_grid(Network ~ Season_num ) +
           my_theme +
           theme(legend.position = "none") +
           ggtitle("S1-S2 Trends for All Shows (LS Rebase)"),
           width = 750,
           height = 1000)
```

```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           stat_smooth(aes(x = Episode_num, y = LS_Rebase, color = Show_Name), 
                       geom = "line", se = F, method = "lm", alpha = 0.5) + 
           stat_smooth(aes(x = Episode_num, y = LS_Rebase), 
                       geom = "line", color = "black", se = F, 
                       method = "lm", linetype = "dashed", alpha = 0.7) +
           facet_grid(Network ~ Season_num ) +
           my_theme +
           theme(legend.position = "none") +
           ggtitle("S1-S2 Linear Trends for All Shows (LS Rebase)"),
           width = 750,
           height = 1000)
```

S1-S2 Trends for All Networks (LS Rebase, Episode Average)
```{R}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                  group_by(Network, Season_num, Episode_num) %>% 
                  summarise(avg_rebase = mean(LS_Rebase))) + 
           geom_point(aes(x = Episode_num, y = avg_rebase, color = Network)) + 
           geom_line(aes(x = Episode_num, y = avg_rebase, color = Network)) + 
           geom_line(data = (df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3) %>% 
                               group_by(Season_num, Episode_num) %>% 
                               summarise(avg_rebase = mean(LS_Rebase))), 
                     aes(x = Episode_num, y = avg_rebase), color = "black", linetype = "dashed") + 
           scale_y_continuous(labels = comma) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Trends for All Networks (LS Rebase, Episode Average)") +
           my_theme,
           width = 1000,
           heght = 750)
```

S1-S2 Linear Trends for All Networks (LS Rebase)
```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) +
  geom_jitter(aes(x = Episode_num, y = LS_Rebase, color = Network), alpha = 0.35) +
  geom_smooth(aes(x = Episode_num, y = LS_Rebase, color = Network), se = F, method = lm) +
  geom_smooth(aes(x = Episode_num, y = LS_Rebase), color = "black", se = F, method = lm,
              linetype = "dashed") +
  coord_cartesian(ylim = c(-250000, 250000)) +
  scale_y_continuous(labels = comma) +
  facet_wrap(~Season_num) +
  ggtitle("S1-S2 Linear Trends for All Networks (LS Rebase)") +
  my_theme,
  width = 1000,
  height = 750)
  
```

S1-S2 Smooth Trends for All Networks (LS Rebase)
```{r}
ggplotly(ggplot(df %>% filter(Episode_num < 15 & Season_num > 0 & Season_num <3)) + 
           geom_jitter(aes(x = Episode_num, y = LS_Rebase, color = Network), alpha = 0.35) + 
           geom_smooth(aes(x = Episode_num, y = LS_Rebase, color = Network), se = F) + 
           geom_smooth(aes(x = Episode_num, y = LS_Rebase), 
                       color = "black", se = F, linetype = "dashed") + 
           coord_cartesian(ylim = c(-500000, 500000)) +
           scale_y_continuous(labels = comma) +
           facet_wrap(~Season_num) +
           ggtitle("S1-S2 Smooth Trends for All Networks (LS Rebase)") +
           my_theme,
           width = 1000,
           height = 750)
```